The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex
intro words

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}
\newcommand{\exosyspop}{\project{exosyspop}}

@@

% EB catalog: \citep{Kirk:2016}

% Microlensing OR: \citep{Shvartzvald:2016}

Data from the \kepler\ Mission has been used to discover thousands of
transiting exoplanets.
The systematic nature of these discoveries and careful quantification of
survey selection effects, search completeness, and catalog reliability has
enabled many diverse studies of the detailed frequency and distribution of
exoplanets \citep[for example,][]{Howard:2012, Petigura:2013,
Foreman-Mackey:2014, Dressing:2015, Burke:2015, Mulders:2015}.
So far, these results have been limited to relatively short orbital periods
because existing transit search methods require the observation of multiple
transits within the baseline of the data.
For \kepler, with a baseline of about four years, this sets an absolute upper
limit on the detectable periods of about two years.
In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, an exo-Jupiter would be missed by most existing transit search
procedures.

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[RV; for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.

It is possible to discover long-period planets like this using targeted radial
velocity (RV) surveys

but the cost of implementing a systematic RV search is
substantially higher than searching the existing and forthcoming photometric
data for single transits.

@@

\begin{floattable}
\begin{deluxetable}{ccc}
\tabletypesize{\footnotesize}
\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
\include{ortab}
\tablenotetext{a}{See \eq{rate-density}}
\tablecomments{These values are computed in the period range 2--25~years.}
\end{deluxetable}
\end{floattable}

>>>>

% Projects:
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\plato}{\project{PLATO}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\bls}{\project{BLS}}
\newcommand{\emcee}{\project{emcee}}
\newcommand{\exosyspop}{\project{exosyspop}}

@@

Data from the \kepler\ Mission \citep{Borucki:2011} has been used to discover
thousands of transiting exoplanets.
The systematic nature of these discoveries and careful quantification of
survey selection effects, search completeness, and catalog reliability has
enabled many diverse studies of the detailed frequency and distribution of
exoplanets \citep[for example,][]{Howard:2012, Petigura:2013,
Foreman-Mackey:2014, Dressing:2015, Burke:2015, Mulders:2015}.
So far, these results have been limited to relatively short orbital periods
because existing transit search methods require the observation of at least
three transits within the baseline of the data.
For \kepler, with a baseline of about four years, this sets an absolute upper
limit on the detectable periods of about two years.
In the Solar System, Jupiter~--~with a period of 12 years~--~dominates the
planetary dynamics and, since it would only exhibit at most one transit in the
\kepler\ data, an exo-Jupiter would be missed by most existing transit search
procedures.

Before the launch of the \kepler\ Mission, it was predicted that the nominal
mission would discover at least 10 exoplanets with only one or two observed
transits \citep{Yee:2008} and subsequent searches for these signals have
already been more fruitful than expected \citep{Wang:2015, Uehara:2016}.
However, the systematic study of the population of long-period exoplanets
found in the \kepler\ data has, so far, been limited because of the
substantial technical challenge and the subtleties of interpretation.
Any single transit events discovered in the \kepler\ light curves are
interesting in their own right but the development of a method for the
discovery of planets with orbital periods longer than the survey baseline are
crucial for the future of the study of exoplanets via the transit method.
All future transit surveys have shorter observational baselines than the
\kepler\ Mission (\KT, \citealt{Howell:2014}; \tess, \citealt{Ricker:2015};
\plato, \citealt{Rauer:2014}).
The methodology presented in the following pages can be modified to be applied
to these forthcoming data sets as they are collecting in the upcoming years.

A study of the population of long-period transiting planets complements
parallel radial velocity \citep[RV; for example][]{Cumming:2008,
Knutson:2014, Bryan:2016}, microlensing \citep[for
example][]{Gould:2010, Cassan:2012, Clanton:2014, Shvartzvald:2016}, and
direct imaging \citep[for example][]{Bowler:2016}.
Exoplanets with both mass and radius measurements can be used to study
planetary compositions and the formation of planetary systems \citep[for
example][]{Weiss:2014, Rogers:2015, Wolfgang:2016}.
The existing catalog of exoplanets with measured densities is sparsely
populated at long orbital periods and discoveries with the transit method are
compelling targets for follow-up observations.
Furthermore, even at long orbital periods, the \kepler\ light curves should be
sensitive to smaller planets than the current state-of-the-art RV surveys.

@@

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
\include{ortab}
\tablenotetext{a}{$\Gamma_V = \dd^2 N/\dd\ln P\dd\ln R$; see \eq{rate-density}}
\tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
positive}
\tablecomments{These values are computed in the period range 2--25~years.}
\end{deluxetable}
\end{floattable}
